### 2013-09-03 exact_learning/paper.tex
more on algorithms for structured learning, but broke the algorithm listings?
FIX put chapter commands in separate files, so that the text is not on a new page...
slight improvement of organization and introduction of exact learning chapter

\section{Introduction}
% Remove duplication with pystruct intro
As discussed previously, many computer vision algorithms empoy conditional random
field models on pixel or superpixel graphs. These graphs by nature contain loops,
making exact prediction and loss-augmented prediction intractable.
As loss-augmented prediction is a centreal step in the learning algorithms
discussed in Chapter~\ref{ch:structured_pystruct}
in the inference then lead to approximate learning.

In this chapter, we investigate the impact of these approximations in
the one-slack learning algorithms in the context of semantic 
image segmentation. We show that despite inference being deemed intractable in
loopy superpixel models, we are able to learn a structured support vector machine
for this application exactly.
learning a model of pairwise
We will evaluate our approach on the popular MSRC-21 and Pascal VOC datasets.

The contribution of this chapter is threefold:
\begin{itemize}
    \item We analyze the simultaneous use of multiple approximate inference
        methods for learning SSVMs using the cutting plane method, relating
        approximate learning to the exact optimum.
    \item We introduce an efficient caching scheme to accelerate cutting plane
        training.
    \item We demonstrate that using a combination of under-generating and exact
        inference methods, we can learn an SSVM exactly in a practical
        application, even in the presence of loopy graphs.
\end{itemize}

@@

Max margin learning for structured prediction was introduced by
\citet{taskar2003max}, in the form of maximum-margin Markov models. Later, this
framework was generalized to structural support vector machines by
\citet{tsochantaridis2006large}. Both works assume tractable loss-augmented
inference.

Currently the most widely used method is the one-slack cutting plane formulation
introduced by \citet{joachims2009cutting}.
This work also introduced the caching of constraints,
which serves as a basis for our work. We improve upon their caching scheme, and in
particular consider how it interacts with approximate inference algorithms.

% TODO learning for inference?
Recently, there has been much research in learning structured prediction models
where standard exact inference techniques are not applicable.
The influence of approximate inference on structural support vector machine
learning was first analyzed by  \citet{finley2008training}.
\citet{finley2008training} show convergence results for under-generating and
over-generating inference procedures, meaning methods that find suboptimal, but
feasible solutions, and optimal solutions from a larger (unfeasible) set,
respectively.
\citet{finley2008training} demonstrate that over-generating approaches---in
particular linear programming (LP)---perform best on the considered model.
They also give a bound on the empirical risk for this case.
In contrast, we aim at optimizing the non-relaxed objective directly, yielding
the original, tighter bound.

@@

Recently, \citet{meshi2010learning}, \citet{hazan2010primal} and
\citet{komodakis2011efficient} introduced formulations for joint inference and
learning using duality.
In particular, \citet{hazan2010primal} demonstrate the performance of their
model on an image denoising task, where it is possible to learn a large number
of parameters efficiently.
While these approaches show great promise, in particular for pixel-level or
large-scale problems, they perform approximate inference and learning, and do
not relate their results back to the original SSVM objective they approximate.

\begin{algorithm*}[t]
    \caption{Cutting Plane Training of Structural SVMs \label{alg_cutting_plane}}

\begin{algorithmic}[1]
    \Require Training samples $\{ (x^{1}, y^{1}), \dots, (x^{n}, y^{n})\}$, regularization parameter $C$, stopping tolerance $\epsilon$, separation oracle $I$.
    \Ensure Parameters $\theta$, slack $\xi$
    \State $\W \leftarrow \emptyset$
    \Repeat
    \State $(\theta, \xi) \leftarrow \displaystyle \argmin_{\theta, \xi} \frac{||\theta||}{2}^2 + C \xi$\label{restricted}\\
    \begin{equation*}
        \text{s.t. }\forall \hat{\mathbf{y}}=(\hat{y}^1, \dots, \hat{y}^n) \in \W:
        \left \langle \theta, \sum_{i=1}^n [\psi(x^i, y^i) - \psi(x^i,
            \hat{y}^i)] \right \rangle \geq \sum_{i=1}^n \Delta(y^i, \hat{y}^i)
            - \xi
    \end{equation*}
    \For {i=1, \dots, n}
    \State
    $\hat{y}^i \leftarrow I(x^i, y^i, \theta) \approx \displaystyle \argmax_{\hat{y}\in\mathcal{Y}} \sum_{i=1}^n \Delta(y^i, \hat{y}) - \left \langle \theta, \sum_{i=1}^n [\psi(x^i, y^i) - \psi(x^i, \hat{y})] \right \rangle$ \label{get_cutting_plane}
    \EndFor
    \State $\W \leftarrow \W \cup \{ (\hat{y}^1, \dots, \hat{y}^n) \} $
    \State $ \displaystyle \xi' \leftarrow  \sum_{i=1}^n \Delta(y^i, \hat{y}^i) - \left \langle \theta, \sum_{i=1}^n [\psi(x^i, y^i) - \psi(x^i, \hat{y}^i)] \right \rangle$
    \Until $\xi' - \xi < \epsilon$ \label{convergence_check}
\end{algorithmic}
\end{algorithm*}

There are two groups of inference procedures, as identified in
\citet{finley2008training}: under-generating and over-generating approaches.
An under-generating approach satisfies $I(x^i, y^i, \theta) \in
\mathcal{Y}$, but does not guarantee maximality in line~\ref{get_cutting_plane}
of Algorithm~\ref{alg_cutting_plane}. An over-generating approach on the other
hand, will solve the loss-augmented inference in line~\ref{get_cutting_plane}
exactly, but for a larger set $\hat{\mathcal{Y}} \supset \mathcal{Y}$, meaning
that possibly $I(x^i, y^i, \theta) \notin \mathcal{Y}$.  We will elaborate on
the properties of under-generating and over-generating inference procedures in
Section~\ref{bounds}.

@@

\section{Experiments}
\subsection{Inference Algorithms}
As a fast under-generating inference algorithm, we used $\alpha$-expansion
moves based on non-submodular graph-cuts using Quadratid Pseudo-Boolean
Optimization (QPBO)~\citep{rother2007optimizing}.  This move-making strategy
can be seen as a simple instantiation of the more general framework of fusion
moves, as introduced by \citet{lempitsky2010fusion}

@@

\subsection{Image Segmentation}
We choose superpixel-based semantic image segmentation as sample application
for this work.  CRF based models have a history of success in this application,
with much current work investigating models and
learning~\citep{gonfaus2010harmony, lucchi2013learning, ladicky2009associative,
kohli2009robust, krahenbuhl2012efficient}.  We use the MSRC-21 and Pascal VOC 20120 datasets, two
widely used benchmark in the field.

>>>>

\chapter{Efficient Exact Learning of Loopy CRFs}

\section{Introduction}
% Remove duplication with pystruct intro
As discussed previously, %TODO in the introduction? in pystruct chapter?
 many computer vision algorithms employ conditional random
field models on pixel or superpixel graphs. These graphs, by nature, contain loops,
making exact prediction and loss-augmented prediction in general intractable.
As loss-augmented prediction is a central step in the learning algorithms
discussed in Chapter~\ref{ch:structured_pystruct}
in the inference lead to only approximate learning.

In this chapter, we investigate the necessity and consequences of these
approximations in the one-slack learning algorithms in the context of semantic
image segmentation. We show that despite inference being deemed intractable in
loopy superpixel models, we are able to learn a pairwise conditional random
field model using a structured support vector machine exactly for this task.
We evaluate our approach on the popular MSRC-21 and Pascal VOC datasets. % and nyu?

The contribution of this chapter is threefold:
\begin{itemize}
    \item We analyze the simultaneous use of multiple approximate inference
        methods for learning SSVMs using the cutting plane method, relating
        approximate learning to the exact optimum.
    \item We introduce an efficient caching scheme to accelerate cutting plane
        training.
    \item We demonstrate that using a combination of under-generating and exact
        inference methods, we can learn an SSVM exactly in a practical
        application, even in the presence of loopy graphs.
    % also fusion moves is pretty good?
\end{itemize}

@@

%Max margin learning for structured prediction was introduced by
%\citet{taskar2003max}, in the form of maximum-margin Markov models. Later, this
%framework was generalized to structural support vector machines by
%\citet{tsochantaridis2006large}. Both works assume tractable loss-augmented
%inference.

%Currently the most widely used method is the one-slack cutting plane formulation
%introduced by \citet{joachims2009cutting}.
%This work also introduced the caching of constraints,
%which serves as a basis for our work. We improve upon their caching scheme, and in
%particular consider how it interacts with approximate inference algorithms.

Recently, there has been much research in learning structured prediction models
where standard exact inference techniques are not applicable.
The influence of approximate inference on structural support vector machine
learning was first analyzed by  \citet{finley2008training}.
\citet{finley2008training} show convergence results for under-generating and
over-generating inference procedures, meaning methods that find suboptimal, but
feasible solutions, and optimal solutions from a larger (unfeasible) set,
respectively.
\citet{finley2008training} demonstrate that over-generating approaches---in
particular linear programming (LP)---perform best on the considered model.
They also show that learning parameters with the LP relaxation minimizes a
bound on the empirical risk when extending the target domain to the relaxed
solutions.
In contrast, we aim at optimizing the non-relaxed objective directly, minimizing
the original empirical risk. This is an important difference, as relaxed solutions
are usually not acceptable in practice.

@@

Recently, \citet{meshi2010learning}, \citet{hazan2010primal} and
\citet{komodakis2011efficient} introduced formulations for joint inference and
learning using duality.
In particular, \citet{hazan2010primal} demonstrate the performance of their
model on an image denoising task, where it is possible to learn a large number
of parameters efficiently.
While these approaches show great promise, in particular for pixel-level or
large-scale problems, they perform approximate inference and learning, and do
not relate their results back to the original SSVM objective they approximate.
It is unclear how they compare to standard structured prediction approaches
on real-world applications.

\section{Learnint Structure Support Vector Machines with Approximate Inference}
%TODO ueberleitung zu approximate inference
% wir machen one-slack und I ist jetzt das und das.
There are two groups of inference procedures, as identified in
\citet{finley2008training}: under-generating and over-generating approaches.
An under-generating approach satisfies $I(x^i, y^i, \theta) \in
\mathcal{Y}$, but does not guarantee maximality in line~\ref{get_cutting_plane}
of Algorithm~\ref{alg_cutting_plane}. An over-generating approach on the other
hand, will solve the loss-augmented inference in line~\ref{get_cutting_plane}
exactly, but for a larger set $\hat{\mathcal{Y}} \supset \mathcal{Y}$, meaning
that possibly $I(x^i, y^i, \theta) \notin \mathcal{Y}$.  We will elaborate on
the properties of under-generating and over-generating inference procedures in
Section~\ref{bounds}. %TODO Filler sentence? wat?

@@

\section{Experiments}

\subsection{Inference Algorithms}

As a fast under-generating inference algorithm, we used $\alpha$-expansion
moves based on non-submodular graph-cuts using Quadratid Pseudo-Boolean
Optimization (QPBO)~\citep{rother2007optimizing}.  This move-making strategy
can be seen as a simple instantiation of the more general framework of fusion
moves, as introduced by \citet{lempitsky2010fusion}

@@

\subsection{Image Segmentation}
We use superpixel-based semantic image segmentation as our application as this is our task of interest. %TODO formulation
for this work.  CRF based models have a history of success in this application,
with much current work investigating models and
learning~\citep{gonfaus2010harmony, lucchi2013learning, ladicky2009associative,
kohli2009robust, krahenbuhl2012efficient}.  We use the MSRC-21 and Pascal VOC 20120 datasets, two
widely used benchmark in the field.
